SubsidyExplorer - Step 4: Apply proposal 'definitions' to vessel list

### 2020-08-15 scripts/05_subsidy_reform_definitions.Rmd

# Paths to other data files
iuu_dat_path <- here::here("data", "raw", "IUU-Vessel-List-2019", "IUUList-20190430.csv")
costello_2016_path <- here::here("data", "edited", "costello_et_al_2016_upsides_tidy.csv")
eez_info_path <- here::here("data", "lookup-tables", "eez_info.csv")

@@

# Extract only vessels currently listed, and create a new entry for each using the "name" field
iuu_clean_name <- iuu_list %>% 
   dplyr::filter(currently_listed) %>%
   mutate(name_new = str_split(name, ", "))%>%
   unnest(cols = c(name_new)) %>%
  dplyr::select(name, name_new, imo, gear_type, flag, ircs, ssvid, gt, length) %>%
  mutate(n_shipname = map_chr(name_new, normalize_shipname))

@@

```{r}
# Load costello data to get the fraction of catches by eez/fao region that are in RAM and are determined to be overfished
costello_2016_dat <- read_csv(costello_2016_path) %>%
  clean_names(case = "snake")

@@

# Match
eez_ram_stocks <- eez_ram_stocks %>%
  left_join(eez_effort, by = c("iso3" = "eez_territory1_iso3", "region_fao_split" = "fao_region")) %>%
  group_by(eez_id, region_fao_split) %>%
  summarize(n_stocks = n_distinct(id_orig),
            mean_bv_bmsy = mean(bv_bmsy, na.rm = T),
            median_bv_bmsy = mean(bv_bmsy, na.rm = T),
            w_mean_bv_bmsy = weighted.mean(bv_bmsy, w = (msy/n_regions), na.rm = T)) %>%
  mutate(oa1_median = ifelse(median_bv_bmsy >= 1, F, T),
         oa1_w_mean = ifelse(w_mean_bv_bmsy >= 1, F, T),
         oa2_median = ifelse(median_bv_bmsy >= 0.8, F, T),
         oa2_w_mean = ifelse(w_mean_bv_bmsy >= 0.8, F, T)) %>%
  dplyr::select(eez_id, region_fao_split, oa1_median, oa1_w_mean, oa2_median, oa2_w_mean)

@@

# Get statuses of domestic stocks by flag state and fao region
eez_stocks <- costello_2016_dat %>%
  dplyr::filter(!is.na(iso3)) %>%
  left_join(eez_effort, by = c("iso3" = "eez_territory1_iso3", "region_fao_split" = "fao_region")) %>%
  group_by(eez_id, region_fao_split) %>%
  summarize(n_stocks = n_distinct(id_orig),
            mean_bv_bmsy = mean(bv_bmsy, na.rm = T),
            median_bv_bmsy = mean(bv_bmsy, na.rm = T),
            w_mean_bv_bmsy = weighted.mean(bv_bmsy, w = (msy/n_regions), na.rm = T)) %>%
  mutate(oa3_median = ifelse(median_bv_bmsy >= 1, F, T),
         oa3_w_mean = ifelse(w_mean_bv_bmsy >= 1, F, T),
         oa4_median = ifelse(median_bv_bmsy >= 0.8, F, T),
         oa4_w_mean = ifelse(w_mean_bv_bmsy >= 0.8, F, T)) %>%
  dplyr::select(eez_id, region_fao_split, oa3_median, oa3_w_mean, oa4_median, oa4_w_mean)

>>>>

# Paths to other data files
iuu_dat_path <- here::here("data", "raw", "combined-IUU-vessel-list", "IUUList-20190430.csv")
costello_2016_path <- here::here("data", "edited", "costello_et_al_2016_upsides_tidy.csv")
ram_dat_path <- here::here("data", "edited", "RAMLDB_v4.491_bvmsy_tidy.csv")
eez_info_path <- here::here("data", "lookup-tables", "eez_info.csv")

@@

# Extract only vessels currently listed, and create a new entry for each using the "name" field
# We also normalize shipname using the same function GFW uses to normalize their shipnames (ignore roman numeral error - double checked this and it's working fine)
iuu_clean_name <- iuu_list %>% 
   dplyr::filter(currently_listed) %>%
   mutate(name_new = str_split(name, ", "))%>%
   unnest(cols = c(name_new)) %>%
  dplyr::select(name, name_new, imo, gear_type, flag, ircs, ssvid, gt, length) %>%
  mutate(n_shipname = map_chr(name_new, normalize_shipname))

@@

```{r}
# Load RAM data to get the status of stocks
costello_2016_dat <- read_csv(costello_2016_path) %>%
  clean_names(case = "snake")

@@

# Match
eez_ram_stocks <- eez_ram_stocks %>%
  left_join(eez_effort, by = c("iso3" = "eez_territory1_iso3", "region_fao_split" = "fao_region")) %>%
  group_by(eez_id, region_fao_split) %>%
  summarize(n_stocks = n_distinct(id_orig),
            mean_bv_bmsy = mean(bv_bmsy, na.rm = T),
            median_bv_bmsy = mean(bv_bmsy, na.rm = T),
            w_mean_bv_bmsy = weighted.mean(bv_bmsy, w = (msy/n_regions), na.rm = T)) %>%
  ungroup() %>%
  mutate(oa1_median = ifelse(median_bv_bmsy >= 1, F, T),
         oa1_w_mean = ifelse(w_mean_bv_bmsy >= 1, F, T),
         oa2_median = ifelse(median_bv_bmsy >= 0.8, F, T),
         oa2_w_mean = ifelse(w_mean_bv_bmsy >= 0.8, F, T)) %>%
  dplyr::select(eez_id, region_fao_split, oa1_median, oa1_w_mean, oa2_median, oa2_w_mean)

@@

# Get statuses of domestic stocks by flag state and fao region
eez_stocks <- costello_2016_dat %>%
  dplyr::filter(!is.na(iso3)) %>%
  left_join(eez_effort, by = c("iso3" = "eez_territory1_iso3", "region_fao_split" = "fao_region")) %>%
  group_by(eez_id, region_fao_split) %>%
  summarize(n_stocks = n_distinct(id_orig),
            mean_bv_bmsy = mean(bv_bmsy, na.rm = T),
            median_bv_bmsy = mean(bv_bmsy, na.rm = T),
            w_mean_bv_bmsy = weighted.mean(bv_bmsy, w = (msy/n_regions), na.rm = T)) %>%
  ungroup() %>%
  mutate(oa3_median = ifelse(median_bv_bmsy >= 1, F, T),
         oa3_w_mean = ifelse(w_mean_bv_bmsy >= 1, F, T),
         oa4_median = ifelse(median_bv_bmsy >= 0.8, F, T),
         oa4_w_mean = ifelse(w_mean_bv_bmsy >= 0.8, F, T)) %>%
  dplyr::select(eez_id, region_fao_split, oa3_median, oa3_w_mean, oa4_median, oa4_w_mean)
